Testing Methodologies for Asynchronous Centralized Simulations\\

### 2020-12-03 paper/PaperDraft2.tex
Paper Update

These are all concerns of NodeTank. While they may be to a lesser degree, as NodeTank is a game rather than a tool for executing experiments for research, they will be valid concerns
 to the degree of their perceptibility. As delays grow, corresponds to the players’ abilities to enjoy the experience decline.

@@

\begin{figure}[htbp]
\centerline{\includegraphics [width = 9cm, height = 5cm] {NetworkArchitecture.jpg}}
\caption{Example of a peer to peer and client server architecture}
\end{figure}

Another type of network architecture exists which has one server serve multiple clients, client-server(Fig. 1). In this type of architecture, one node is designated as the server,
and all authoritative communication is handled through it before being sent to the clients[6]. As noted in Fig 1, we can see that any number of clients may connect to the server
at any one time, and clients do not have to be fully connected since the server is the authoritative source. The client-server architecture will be the target of our testing methodologies
and framework. Although peer-peer has its own valid use cases, it is not appropriate for a centralized simulation and would likewise necessitate a different approach to testing.

@@

@@

With the all of the prerequisite work complete, the implementation of the the game and protocol will be discussed. For reference,
the project code is located at (https://github.com/spac3nerd/CSI-5390Proj). The nodejs server
will need to run both traditional HTTP transactons and socket transactions. The HTTP transactions are used to ask the server if
there are any open spots in the game, and whether access is granted to a new player. If access is granted, then the server will return
an unique token to the client with which a socket connection can be requested. The client then requests entry into the game
with the token and a tunnel is established between the client and the server.

In the following sections we will cover the specific testing implementations with the goal of addressing the problem of rigorously testing NodeTank, or any
other multiplayer game built on the NodeJS platform.

@@

\subsection{Remote Testing}

\subsubsection{Core RPC Services}Remote testing of the target application is achieved through an adaptable and extensible pair of RPC services. Two APIs, 'Data' and 'RemoteCtrl', that enable remote testing and they are capable of being updated and expanded quite easily as the application's range of behaviors grow during its lifetime. Each API service is defined in an IDL(Interface Description Language) file. Each defines the a service's name followed by generic a list call signatures of the functions that shoould be exposed by the service. The IDL offers several plain data types such booleans, floating points, a string type, and signed integers of the typical varying bit-widths. Basic C-style structures and enumerations may also be defined to add versatility to the services defined types.
\subsubsection{RPC Adaptability}As the application grows and new types of interactions and information need to be handled, the same pair of IDL need only minor editing by the maintainer. Automatic generations scripts may be rerun at each stage of changing demand. The resulting output is a fully-formed supporting library in the target programming language of choice for, both, the client and server sides of each RPC service. The RPC-server half of each API is included and/or linked to from the simulation's server to allow both services awareness of and access to all necessary data of the simulation's clients. In the event of new or changing data types, the client simulation needs only to be rebuilt in the case of a compiled-language and no changes are required for interpreted languages. In the case of new or changing functions, the auto-generated RPC handlers need only be given function bodies by the tester. Building remote testing utilities for the simulation is easily done thanks to this process, as there are no dependencies between the programming language of the simulation's server and the RPC client. The RPC service itself manages all translation between native data types of the server and it's RPC client. This means the RPC service manages the serialization/deserialization and transport of all function arguments and return values, byte-order translation between differing host hardware, and member alignment between differing host operating environments. All these features allow for a simulation written in javascript, C++, Java, Python, C\#, etc. to agnostically cooperate with any client written in any other supported language and host operating environemnt.
\subsubsection{Distributibility}With an underlying TCP or UDP transport layer, this remote testing strategy allows for a wide range of geographical testing configurations to be thuroughly explored. Testing and examination of the system may be performed in a close-proximity LAN configuration, or the simulation server and its clients may be much more georgraphically separated, communicating over the Internet with one another and the testing client itself.

\section{Case Study}
\subsection{Remote RPC Services}
\subsubsection{Remote Testing Service}
\paragraph{Hooks into the javascript testing framework}
\subsubsection{Remote Control Service}
\paragraph{Injecting user input}
\paragraph{Extracting the rendered environment}

\section{Conclusion}
\subsection{Future Work}

@@

\section{References}
[1] A. Valadares, “Aspect-oriented architectural style for distributed interactive simulations”, 2016,
Available from ProQuest Dissertations \& Theses Global. (1881527059).
Retrieved from https://search-proquest-com.huaryu.kl.oakland.edu/docview/1881527059?accountid=12924

@@

[6] J. Smed, “Aspects of Networking in Multiplayer Computer Games“, Proceedings of International Conference on Application and Development of Computer Games in the 21st Century, Hong Kong, 2001,
Available: https://www.researchgate.net/publication/269251176\_Aspects\_of\_Networking\_in\_Multiplayer\_Computer\_Games
\end{document}

>>>>

These are all concerns of our case study, NodeTank. While they may be to a lesser degree, as NodeTank is a game rather than a tool for executing experiments for research, they will be valid concerns
 to the degree of their perceptibility. As delays grow, corresponds to the players’ abilities to enjoy the experience decline.

\section{Background}

Before we may continue to discuss testing methodologies for centralized simulations, we should take a look at what exactly a centralized asynchronous simulation is. 
In this section, we will take a look at the high-level overview of such a simulation before delving into the specific type of data utilized by NodeTank.

@@

\begin{figure}[htbp]
\centerline{\includegraphics [width = 9cm, height = 5cm] {NetworkArchitecture.jpg}}
\caption{Example of a Client-Server and Peer-Peer Architecture}
\end{figure}

Another type of network architecture exists which has one server serve multiple clients, client-server(Fig. 1). In this type of architecture, one node is designated as the server,
and all authoritative communication is handled through it before being sent to the clients[6]. As noted in Fig 1, we can see that any number of clients may connect to the server
at any one time, and clients do not have to be fully connected since the server is the authoritative source. The client-server architecture will be the target of our testing methodologies
and framework. Although peer-peer has its own valid use cases, it is not appropriate for a centralized simulation and would likewise necessitate a different approach to testing, and thus,
the remainder of this paper will serve a client-server architecture.

With the type of architecture selected, the only remaining task is to introduce the mechanism by which one node communicates with another node. For example, we must answer
the question of how Client 1 and send and receive information from Client 4. Clearly, given that we need to have a centralized simulation, that information must pass through 
the server. The only remaining question is how the server is not only connected to each client, but when that information is to be relayed. There are generally two methods of transmitting
data to and from clients: unicast or broadcast[6]. Fig. 2 demonstrates a high-level overview of the two transmission types.

The main distinction being that unicast allows one node to initate and send some data to a different node while broadcast allows a node to send information to all other nodes at the same time. 
Intuitively, this implies that an unicast approach would have to initiate and conduct as many transactions as there are nodes. Naturally, this does not happen simultaneously and given sufficient nodes,
the probability that the simulation comes out of sync between clients increases. Therefore, since there is only one true simulation in the system, it becomes advantageous to leverage the ability of 
to broadcast a message simultaneously to all other nodes. The advantage of on-time dispatching of data becomes ever more noticeable when dealing with the type of software we will discuss in the case study, multiplayer
games.

\begin{figure}[htbp]
\centerline{\includegraphics [width = 9cm, height = 5cm] {TransmissionArchitecture.jpg}}
\caption{Example of Unicast and Broadcast Transmission Architecture}
\end{figure}

@@

For the goal of developing and testing the game locally on one machine, we will also be able to leverage the fact that it is built to run in the browser on
an interpreted language to run test suites end to end. Firstly, we will investigate an approach similar to Ariyurek et al[2] in order to develop an automated 
system to test the application as well as to automatically find problems with it. Secondly, the fact that the application in its unobstructed build state will have
its internal state visible and inspectable from the outside. That is to say, if we were to run multiple client simulations concurrently, we would be able to inspect 
the state of the simulation on each one of the said client machines independently. This would allow us to inspect the correctness of the model in real time from the 
perspective of each client. Likewise, the fact that we could control each client independently, we will be able to gauge the susceptibility of the simulation to erroneous 
or malicious data by willfully introducing it to one client, and checking if the erroneous data was propagated to the other clients.

@@

@@

\subsection{Trained Model Approach}

Discuss the setup for the trained model - the tools and automatic invocation

\section{Case Study}

With the all of the prerequisite work complete, the implementation of the testing framework for the game and protocol will be discussed. For reference,
the project code is located at (https://github.com/spac3nerd/CSI-5390Proj). The NodeJS server 
will need to run both traditional HTTP transactons and socket transactions. The HTTP transactions are used to ask the server if 
there are any open spots in the game, and whether access is granted to a new player. If access is granted, then the server will return 
an unique token to the client with which a socket connection can be requested. The client then requests entry into the game 
with the token and a tunnel is established between the client and the server. Fig 7. shows the game being played by three players, with
the blue tank being controlled by the current instance.

\begin{figure}[htbp]
\centerline{\includegraphics [width = 9cm, height = 5cm] {GameScreenshot.jpg}}
\caption{Example of Unicast and Broadcast Transmission Architecture}
\end{figure}

Note that each player has his own score count,a representation of all of the other tanks as well as any bullets which were fire, and finally, a chat area
in which any player may type a message to send to all other players at any time. To The full list of rules to the game are as follows:

\begin{itemize}
  \item A Player may move his own tank in any direction at any time.
  \item A Player may aim the tank and fire a bullet at any time.
  \item If a Player's bullet intersects another tank, that tank is destroyed and a point added to Player.
  \item If a Player's tank reaches the red area, their tank will be destroyed and a point deducted.
  \item A Player may send a message to all other players at any time.
\end{itemize}

With all of NodeTank's rules layed out, we have the knowledge necessary to start building up the types of test cases and tests we require. 
In the following sections we will cover the specific testing implementations with the goal of addressing the problem of rigorously testing NodeTank, however, these techniques 
are easily applicable to other multiplayer games built on the NodeJS platform.

\subsection{Automated Client-side Testing}

As mentioned in the Implementation section, each client has either the ability to affect the simulation in some fashion, or is at least capable of receiving an updated
version of the simulation. In the case of NodeTank, each client is responsible for controlling one tank according to the aforementioned rules of the game. As previously mentioned,
instead of simply unit testing in the traditional sense(isolating one function at a time ), but instead attempt to perform a test based upon some use case or rule of the game we will
 benefit from being able to not only test the individual action on one client, but across all clients. Let's take the first rule of the game for example and infer the implications for the entire system 
 of that action being actionable. If a Player A is to move in any direction, then clearly that movement must be rendered in Player A's simuluation at the very least. To allow for interactivity, 
 the movement must be rendered in the simulation of all other players, which implies that the server must correctly receive, process and send a correct update to all players.

 The proposed implementation called for a testing library to be written, which caters to the peculiarities of a case such as NodeTank while providing generalized functionality for all 
 applications of the same architecture. Recall the class diagram in Fig 8. layed out the server-side and client-side classes utilized by the game. The authors have implemented a framework
 under a class entity called "NodeTankTesting", which is coupled into one more more instances of the client-side. The applied changes are visualized in the Fig. 9 daigram. At a high-level,
 the framework provides mechanisms to start up an instance of NodeTank client in the browser, register tests, programatically control a player and assertions to verify the state of each client.

\begin{figure}[htbp]
\centerline{\includegraphics [width = 9cm, height = 5cm] {ClassDiagramWithTesting.jpg}}
\caption{Modified Class Diagram with Testing Framework}
\end{figure}

This testing framework relies on the ability to access the internal state of any client instance of NodeTank. The reader may be interested to know that the author of NodeTank 
elected to utilize the prototype pattern, which is a JavaScript design pattern which allows for great control over inheritance while exposing any closures to outside observers[7]. For example, 
let's take the Game class from the client-side in consideration. In Fig 10. we can see that the variable "game" is defined into two sections: there is a function declaration, whose body functionally 
behaves like a constructor, and a prototype assignment, which is a set of methods inherited by all instances of game. The keen reader will note that this is not quite the same classical inheritance
mechanism utilized by languages such as Java, however we will continue to refer to them as classes as functionally they behave similarly enough.

\begin{figure}[htbp]
\centerline{\includegraphics [width = 9cm, height = 5cm] {GameCodeSnippet.jpg}}
\caption{Snippet of the Game Class}
\end{figure}

The benefit of the prototype pattern is that we are able to inspect the internal state of any game instance running in the brwoser, and we are also able to programatically induce 
any inputs such as movement, firing and entering new chat items. Fig 11. is an example of inspecting the entire instance of NodeTank and the position of the player tank programatically.

\begin{figure}[htbp]
\centerline{\includegraphics [width = 9cm, height = 2.8cm] {GameInspection.jpg}}
\caption{Inspecting an Instance of NodeTank}
\end{figure}

Now that we have a handle to a game instance, we can begin to write some test cases which will allow us to test every client-side functionality of the game. For example, before a player can
connect to the server, the connection must first be negotiated over a HTTP call. The testing framework has a builtin to send the negotiation request along with the player's desired name, and if the 
server is not at the maximum player capacity, it will respond with an unique token which will be used from thereon as an identifier. In order to test this functionality, we can programatically request
the new connection and verify that a token was issued (or denied) as expected. In Fig 12. we can see the implementation of this test - note that "t" refers to the testing framework and that the "requestToken"
function requires that a callback be provided, which is called whenever the response for the token request is received.

\begin{figure}[htbp]
\centerline{\includegraphics [width = 9cm, height = 2.8cm] {TokenTestSnippet.jpg}}
\caption{Snippet of Test Case for Requesting a Token}
\end{figure}

However, a problem remains with this approach in that the test case will work as intended if manually invoked in isolation. Consider that the call itself is asynchronous - we cannot block the 
main (and only) thread on the client-side while we wait for a response to come back from the server, doing so would pause the client-side simulation at every network interaction and there would be no interactivity! 
Suppose that we wish to have an entire suite of tests, and that some of those tests rely on the previous test completing before being invoked. If a string of synchronous function calls would be utilized
in testing, then we would have no mechanism by which to ensure that test B is only called after test A completed if test A is at all asynchronous. Therefore, a more intelligent design pattern must 
be leveraged in order to allow the framework to test all cases automatically. Fig 13. showcases the desired sequence diagram for launching two tests at the correct time without blocking the main thread.

\section{Conclusion}

@@

\section{References}
[1] A. Valadares, “Aspect-oriented architectural style for distributed interactive simulations”, 2016, 
Available from ProQuest Dissertations & Theses Global. (1881527059). 
Retrieved from https://search-proquest-com.huaryu.kl.oakland.edu/docview/1881527059?accountid=12924

@@

[6] J. Smed, “Aspects of Networking in Multiplayer Computer Games“, Proceedings of International Conference on Application and Development of Computer Games in the 21st Century, Hong Kong, 2001,
Available: https://www.researchgate.net/publication/269251176_Aspects_of_Networking_in_Multiplayer_Computer_Games

[7] A. Osmani "JavaScript Patterns", Book, 2012, Available: https://addyosmani.com/resources/essentialjsdesignpatterns/book/
\end{document}
